Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil

### 2022-12-22 appendix/appendix.Rmd
production version

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
  - Danilo Freire[^danilo]
  - David Skarbek[^david]
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
  - Danilo Freire[^danilo]
  - David Skarbek[^david]
date: December 16, 2022
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: yes
    template: template.latex
---

### 2022-12-22 article/article.tex
production version

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nick Cowen, Daniel J. D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J. Phillips, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments. We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington. This study received IRB approval from Brown University in October 2020 (Protocol 2009002803). Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}. We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.}}

@@

\noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
\vspace{.25cm}

@@

In our first experiment, we used a choice-based conjoint experimental design.
We presented respondents with five pairs of profiles. Each profile consisted of
eight attributes: (1) gender of the crime perpetrator; (2) age of the crime
perpetrator; (3) race of the crime perpetrator; (4) residency of the crime
perpetrator (local or nonlocal); (5) type of offense; (6) gender of the victim
of the crime; (7) age of the crime victim; (8) type of lynching perpetrator.
The attributes and levels are displayed in table \ref{tab:categories}.

>>>>

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nick Cowen, Daniel J. D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J. Phillips, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments. We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington. This study received IRB approval from Brown University in October 2020 (Protocol 2009002803). Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}. We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support. The authors declare that they have no conflict of interest.}}

@@

% \noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
\vspace{.25cm}

@@

In our first experiment, we used a choice-based conjoint experimental design.
We presented respondents with five pairs of profiles. Each profile consisted of
eight attributes: (1) gender of the crime perpetrator; (2) age of the crime
perpetrator; (3) race of the crime perpetrator; (4) residency of the crime
perpetrator (local or nonlocal); (5) type of offense; (6) gender of the victim
of the crime; (7) age of the crime victim; (8) type of lynching perpetrator.
The attributes and levels are displayed in Table \ref{tab:categories}.
